% Awesome Source CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/darwiin/awesome-neue-latex-cv
%
% Author:
% Christophe Roger
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)

%Section: Work Experience at the top
\sectionTitle{Experience}{\faSuitcase}
\begin{experiences}
  \experience{Feb. 2019} {Electronics Engineer II}{Cimarron Energy}{Wheat Ridge, CO}
    {Jul. 2020} {
      \begin{itemize}
        \item Instituted a code review policy.
        \item Created internal production software for programming and verifying a product line.
        \item Refactored codebase to support product variation development.
        \item Involved in the research, planning, and architecture for the next generation product line.
        \item Created a proof of concept for the next generation product line.
        \item Implemented continuous integration with format, lint, unit test, and integration test checks on an in-house server.
        \item Wrote drivers and supporting library code for next generation products.
      \end{itemize}
    }
    {ARM Cortex-M, Atmel Studio, C, C++, C\#, ChibiOS, Clang Tools, FreeRTOS, GitHub, Ubuntu Linux, MbedOS, Python3, Qt, Visual Studio Code, Yocto}
  \emptySeparator
  \experience{Sep. 2014}{Embedded Firmware Engineer | Software Engineer}{Clear Blue Engineering}{Lafayette, CO}
    {Feb. 2019}{
      \begin{itemize}
        \item Created the initial firmware for an embedded device for water sterilization.
        \item Developed the firmware for an ARM based IoT device to measure and control power consumption in residential and commercial settings.
        \item Ported an embedded device to a PIC microcontroller.
        \item Involved i the development of a HIPAA compliant telemedicine application.
        \item Designed and 3D printed manufacturing jigs and fixtures.
        \item Modified a 3D printer to continuously print a single object and deposit it into a bin.
        \item Created the PCB layout for a company Maker Faire project.
      \end{itemize}
    }
    {Android, ARM Cortex-M, BitBucket, C, C++, CircuitMaker, FormLabs, Java, JavaScript, Microchip PIC, MPLAB X, OnShape, Particle.io}
  \emptySeparator
    % make into contract experience, two projects?
  \experience{Feb. 2010}{Software Engineering Contractor}{Clear Blue Engineering}{Lafayette, CO}
    {Jul. 2012}{
      \begin{itemize}
        \item Created an Android application which communicated with a SOAP API backend.
        \item Extended early versions of Android with Arabic text reshaping.
        \item Created a .Net application that communicated with a backing web API and translated received data into a custom format usable by an embedded device.
        \item Interfaced with clients to determine product specifications, design goals, time tables, and bug fixes.
      \end{itemize}
    }
    {Android, C\#, Gson, Java, Visual Studio}
  \emptySeparator
  \experience{Nov. 2005}{Student Data Specialist | Student IT Professor I}{Denning Research Group}{Fort Collins, CO}
    {May 2009}{
      \begin{itemize}
        \item Maintained computing resources including storage servers, computing clusters, and NFS servers.
        \item Helped design a new computing cluster according to requirements set by the research group.
        \item Helped transition servers to use LDAP authentication.
        \item Increased storage capacity to meet the growing demand for larger cluster output data.
        \item Reorganized network switches to increase throughput, provide fault tolerance, and make management easier.
        \item Upgraded servers with lights-out management functionality.
      \end{itemize}
    }
    {DRBD, CentOS Linux, Debian Linux, LDAP, NFS, Sun Grid Engine}
\end{experiences}
